---
title: "NFLFastR"
output: html_document
date: "2024-10-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Installing Packages:

```{r}
#install.packages("tidyverse", type = "binary")
#install.packages("ggrepel", type = "binary")
#install.packages("nflreadr", type = "binary")
#install.packages("nflplotR", type = "binary")
#install.packages("gsisdecoder")
#install.packages("slider")
#install.packages("car")
```


Collecting the Data

```{r}
library(slider)
library(nflfastR)
library(dplyr, warn.conflicts = FALSE)
library(gsisdecoder)
library(car)
ids <- nflfastR::fast_scraper_schedules(2017:2019) %>%
  dplyr::filter(game_type == "SB") %>%
  dplyr::pull(game_id)
pbp <- nflfastR::build_nflfastR_pbp(ids)
```


## Loading PBP Data


```{r}
data_2024 <- load_pbp(2024)
  data_2024$season <- 2024
data_2023 <- load_pbp(2023)
  data_2023$season <- 2023
data_2022 <- load_pbp(2022)
  data_2022$season <- 2022
data_2021 <- load_pbp(2021)
  data_2021$season <- 2021
data_2020 <- load_pbp(2020)
  data_2020$season <- 2020
data_2019 <- load_pbp(2019)
  data_2019$season <- 2019
data_2018 <- load_pbp(2018)
  data_2018$season <- 2018
data_2017 <- load_pbp(2017)
  data_2017$season <- 2017


pbp_data <- rbind(data_2024,data_2023,data_2022,data_2021,data_2020,data_2019,data_2018,data_2017)
#View(pbp_data)
```


### Creating the Schedule ###


```{r}
schedule_data_2024 <- fast_scraper_schedules(2024)
schedule_data_2023 <- fast_scraper_schedules(2023)
schedule_data_2022 <- fast_scraper_schedules(2022)
schedule_data_2021 <- fast_scraper_schedules(2021)
schedule_data_2020 <- fast_scraper_schedules(2020)
schedule_data_2019 <- fast_scraper_schedules(2019)

schedule_data <- rbind(schedule_data_2024,schedule_data_2023,schedule_data_2022,schedule_data_2021,
                       schedule_data_2020,schedule_data_2019)

#View(schedule_data)
```


### Creating synthetic data ###


```{r}
test_sch <- schedule_data %>% select("game_id","season","week","gameday","away_team","home_team")

test_sch <- rename(test_sch, "game_date" = "gameday")

# Create the desired structure
expanded_df <- test_sch %>%
  # Create the first set of rows (home_team as posteam)
  mutate(posteam = home_team, defteam = away_team) %>%
  # Add the second set of rows (away_team as posteam)
  bind_rows(
    test_sch %>%
      mutate(posteam = away_team, defteam = home_team)
  )

pbp_data <- bind_rows(expanded_df, pbp_data)
```


### Team Stats Per Game ###


```{r}
# Add a new column to classify explosive plays
pbp_data <- pbp_data %>%
  mutate(explosive_play = case_when(
    play_type == "run" & yards_gained >= 10 ~ "Explosive Run",
    play_type == "pass" & yards_gained >= 20 ~ "Explosive Pass",
    TRUE ~ "Non-Explosive"
  ))

# Summarize team statistics, focusing on points scored by the team
team_stats_for <- pbp_data %>%
  group_by(posteam, season, week, game_date) %>%
  summarize(
    points_for = max(posteam_score, na.rm = TRUE), # Points scored by the team
    yards_for = sum(yards_gained, na.rm = TRUE),
    plays_for = n(),
    avg_epa_for = mean(epa, na.rm = TRUE),
    success_rate_for = mean(success, na.rm = TRUE),
    pass_attempts_for = sum(play_type == "pass", na.rm = TRUE),
    run_attempts_for = sum(play_type == "run", na.rm = TRUE),
    pass_rate_for = pass_attempts_for / (pass_attempts_for + run_attempts_for),
    ex_runs_for = sum(explosive_play == "Explosive Run"),
    ex_pass_for = sum(explosive_play == "Explosive Pass"),
    ex_plays_for = sum(ex_runs_for + ex_pass_for),
    ex_pct_for = (ex_plays_for / plays_for))

team_stats_against <- pbp_data %>%
  group_by(defteam, season, week, game_date) %>%
  summarize(
    points_against = max(posteam_score, na.rm = TRUE), # Points scored by the team
    yards_against = sum(yards_gained, na.rm = TRUE),
    plays_against = n(),
    avg_epa_against = mean(epa, na.rm = TRUE),
    success_rate_against = mean(success, na.rm = TRUE),
    pass_attempts_against = sum(play_type == "pass", na.rm = TRUE),
    run_attempts_against = sum(play_type == "run", na.rm = TRUE),
    pass_rate_against = pass_attempts_against / (pass_attempts_against + run_attempts_against),
    ex_runs_against = sum(explosive_play == "Explosive Run"),
    ex_pass_against = sum(explosive_play == "Explosive Pass"),
    ex_plays_against = sum(ex_runs_against + ex_pass_against),
    ex_pct_against = (ex_plays_against / plays_against))

#View(team_stats_for)
#View(team_stats_against)

### Merging the Datasets

team_stats <- team_stats_for %>%
  left_join(team_stats_against, by = c("posteam" = "defteam","season" = "season","week" = "week",
                                       "game_date"="game_date"))

#View(team_stats)
```


### Define Functions for Slide_DBL ###


```{r}
#Weighted EPA Against Function
weighted_epaf_function <- function(avg_epa_for, plays_for) {
  sum(avg_epa_for * plays_for) / sum(plays_for)
}

#Weighted EPA Against Function
weighted_epaa_function <- function(avg_epa_against, plays_against) {
  sum(avg_epa_against * plays_against) / sum(plays_against)
}

#Weighted Success Rate For Function
weighted_srf_function <- function(success_rate_for, plays_for) {
  sum(success_rate_for * plays_for) / sum(plays_for)
}

#Weighted Success Rate Against Function
weighted_sra_function <- function(success_rate_against, plays_against) {
  sum(success_rate_against * plays_against) / sum(plays_against)
}

#Weighted Pass Rate For Function
weighted_prf_function <- function(pass_rate_for, pass_attempts_for) {
  sum(pass_rate_for * pass_attempts_for) / sum(pass_attempts_for)
}

#Weighted Pass Rate Against Function
weighted_pra_function <- function(pass_rate_against, pass_attempts_against) {
  sum(pass_rate_against * pass_attempts_against) / sum(pass_attempts_against)
}

#Weighted Ex Play Rate For Function
weighted_xprf_function <- function(ex_pct_for, plays_for) {
  sum(ex_pct_for * plays_for) / sum(plays_for)
}

#Weighted Ex Play Rate Against Function
weighted_xpra_function <- function(ex_pct_against, plays_against) {
  sum(ex_pct_against * plays_against) / sum(plays_against)
}
```


### Creating Rolling Averages ###


```{r}
team_rolling_averages <- team_stats %>%
  arrange(posteam, game_date) %>%
  group_by(posteam) %>%
  mutate(rapf_2W = slide_dbl(points_for, mean, .before = 2, .after = -1, .complete = TRUE),
         rapf_4W = slide_dbl(points_for, mean, .before = 4, .after = -1, .complete = TRUE),
         rapf_8W = slide_dbl(points_for, mean, .before = 8, .after = -1, .complete = TRUE),
         rapf_17W = slide_dbl(points_for, mean, .before = 17, .after = -1, .complete = TRUE),
         rapa_2W = slide_dbl(points_against, mean, .before = 2, .after = -1, .complete = TRUE),
         rapa_4W = slide_dbl(points_against, mean, .before = 4, .after = -1, .complete = TRUE),
         rapa_8W = slide_dbl(points_against, mean, .before = 8, .after = -1, .complete = TRUE),
         rapa_17W = slide_dbl(points_against, mean, .before = 17, .after = -1, .complete = TRUE),
         rayf_2W = slide_dbl(yards_for, mean, .before = 2, .after = -1, .complete = TRUE),
         rayf_4W = slide_dbl(yards_for, mean, .before = 4, .after = -1, .complete = TRUE),
         rayf_8W = slide_dbl(yards_for, mean, .before = 8, .after = -1, .complete = TRUE),
         rayf_17W = slide_dbl(yards_for, mean, .before = 17, .after = -1, .complete = TRUE),
         raya_2W = slide_dbl(yards_against, mean, .before = 2, .after = -1, .complete = TRUE),
         raya_4W = slide_dbl(yards_against, mean, .before = 4, .after = -1, .complete = TRUE),
         raya_8W = slide_dbl(yards_against, mean, .before = 8, .after = -1, .complete = TRUE),
         raya_17W = slide_dbl(yards_against, mean, .before = 17, .after = -1, .complete = TRUE),
         raplf_2W = slide_dbl(plays_for, mean, .before = 2, .after = -1, .complete = TRUE),
         raplf_4W = slide_dbl(plays_for, mean, .before = 4, .after = -1, .complete = TRUE),
         raplf_8W = slide_dbl(plays_for, mean, .before = 8, .after = -1, .complete = TRUE),
         raplf_17W = slide_dbl(plays_for, mean, .before = 17, .after = -1, .complete = TRUE),
         rapla_2W = slide_dbl(plays_against, mean, .before = 2, .after = -1, .complete = TRUE),
         rapla_4W = slide_dbl(plays_against, mean, .before = 4, .after = -1, .complete = TRUE),
         rapla_8W = slide_dbl(plays_against, mean, .before = 8, .after = -1, .complete = TRUE),
         rapla_17W = slide_dbl(plays_against, mean, .before = 17, .after = -1, .complete = TRUE),
         rwepaf_2W=slide_dbl(.x=avg_epa_for,.y=plays_for,.f=~weighted_epaf_function(.x,.y),
                             .before=2,.after=-1,.complete=TRUE),
         rwepaf_4W=slide_dbl(.x=avg_epa_for,.y=plays_for,.f=~weighted_epaf_function(.x,.y),
                             .before=4,.after=-1,.complete=TRUE),
         rwepaf_8W=slide_dbl(.x=avg_epa_for,.y=plays_for,.f=~weighted_epaf_function(.x,.y),
                             .before=8,.after=-1,.complete=TRUE),
         rwepaf_17W=slide_dbl(.x=avg_epa_for,.y=plays_for,.f=~weighted_epaf_function(.x,.y),
                              .before=17,.after=-1,.complete=TRUE),
         rwepaa_2W=slide_dbl(.x=avg_epa_against,.y=plays_against,.f=~weighted_epaa_function(.x,.y),
                             .before=2,.after=-1,.complete=TRUE),
         rwepaa_4W=slide_dbl(.x=avg_epa_against,.y=plays_against,.f=~weighted_epaa_function(.x,.y),
                             .before=4,.after=-1,.complete=TRUE),
         rwepaa_8W=slide_dbl(.x=avg_epa_against,.y=plays_against,.f=~weighted_epaa_function(.x,.y),
                             .before=8,.after=-1,.complete=TRUE),
         rwepaa_17W=slide_dbl(.x=avg_epa_against,.y=plays_against,.f=~weighted_epaa_function(.x,.y),
                              .before=17,.after=-1,.complete=TRUE),
         rwsrf_2W=slide_dbl(.x=success_rate_for,.y=plays_for,.f=~weighted_srf_function(.x,.y),
                            .before=2,.after=-1,.complete=TRUE),
         rwsrf_4W=slide_dbl(.x=success_rate_for,.y=plays_for,.f=~weighted_srf_function(.x,.y),
                            .before=4,.after=-1,.complete=TRUE),
         rwsrf_8W=slide_dbl(.x=success_rate_for,.y=plays_for,.f=~weighted_srf_function(.x,.y),
                            .before=8,.after=-1,.complete=TRUE),
         rwsrf_17W=slide_dbl(.x=success_rate_for,.y=plays_for,.f=~weighted_srf_function(.x,.y),
                             .before=17,.after=-1,.complete=TRUE),
         rwsra_2W=slide_dbl(.x=success_rate_against,.y=plays_against,.f=~weighted_sra_function(.x,.y),
                            .before=2,.after=-1,.complete=TRUE),
         rwsra_4W=slide_dbl(.x=success_rate_against,.y=plays_against,.f=~weighted_sra_function(.x,.y),
                            .before=4,.after=-1,.complete=TRUE),
         rwsra_8W=slide_dbl(.x=success_rate_against,.y=plays_against,.f=~weighted_sra_function(.x,.y),
                            .before=8,.after=-1,.complete=TRUE),
         rwsra_17W=slide_dbl(.x=success_rate_against,.y=plays_against,.f=~weighted_sra_function(.x,.y),
                             .before=17,.after=-1,.complete=TRUE),
         rwprf_2W=slide_dbl(.x=pass_rate_for,.y=pass_attempts_for,.f=~weighted_prf_function(.x,.y),
                            .before=2,.after=-1,.complete=TRUE),
         rwprf_4W=slide_dbl(.x=pass_rate_for,.y=pass_attempts_for,.f=~weighted_prf_function(.x,.y),
                            .before=4,.after=-1,.complete=TRUE),
         rwprf_8W=slide_dbl(.x=pass_rate_for,.y=pass_attempts_for,.f=~weighted_prf_function(.x,.y),
                            .before=8,.after=-1,.complete=TRUE),
         rwprf_17W=slide_dbl(.x=pass_rate_for,.y=pass_attempts_for,.f=~weighted_prf_function(.x,.y),
                             .before=17,.after=-1,.complete=TRUE),
         rwpra_2W=slide_dbl(.x=pass_rate_against,.y=pass_attempts_against,.f=~weighted_pra_function(.x,.y),
                            .before=2,.after=-1,.complete=TRUE),
         rwpra_4W=slide_dbl(.x=pass_rate_against,.y=pass_attempts_against,.f=~weighted_pra_function(.x,.y),
                            .before=4,.after=-1,.complete=TRUE),
         rwpra_8W=slide_dbl(.x=pass_rate_against,.y=pass_attempts_against,.f=~weighted_pra_function(.x,.y),
                            .before=8,.after=-1,.complete=TRUE),
         rwpra_17W=slide_dbl(.x=pass_rate_against,.y=pass_attempts_against,.f=~weighted_pra_function(.x,.y),
                             .before=17,.after=-1,.complete=TRUE),
         raxrf_2W = slide_dbl(ex_runs_for, mean, .before = 2, .after = -1, .complete = TRUE),
         raxrf_4W = slide_dbl(ex_runs_for, mean, .before = 4, .after = -1, .complete = TRUE),
         raxrf_8W = slide_dbl(ex_runs_for, mean, .before = 8, .after = -1, .complete = TRUE),
         raxrf_17W = slide_dbl(ex_runs_for, mean, .before = 17, .after = -1, .complete = TRUE),
         raxpf_2W = slide_dbl(ex_pass_for, mean, .before = 2, .after = -1, .complete = TRUE),
         raxpf_4W = slide_dbl(ex_pass_for, mean, .before = 4, .after = -1, .complete = TRUE),
         raxpf_8W = slide_dbl(ex_pass_for, mean, .before = 8, .after = -1, .complete = TRUE),
         raxpf_17W = slide_dbl(ex_pass_for, mean, .before = 17, .after = -1, .complete = TRUE),
         raxplf_2W = slide_dbl(ex_plays_for, mean, .before = 2, .after = -1, .complete = TRUE),
         raxplf_4W = slide_dbl(ex_plays_for, mean, .before = 4, .after = -1, .complete = TRUE),
         raxplf_8W = slide_dbl(ex_plays_for, mean, .before = 8, .after = -1, .complete = TRUE),
         raxplf_17W = slide_dbl(ex_plays_for, mean, .before = 17, .after = -1, .complete = TRUE),
         raxra_2W = slide_dbl(ex_runs_against, mean, .before = 2, .after = -1, .complete = TRUE),
         raxra_4W = slide_dbl(ex_runs_against, mean, .before = 4, .after = -1, .complete = TRUE),
         raxra_8W = slide_dbl(ex_runs_against, mean, .before = 8, .after = -1, .complete = TRUE),
         raxra_17W = slide_dbl(ex_runs_against, mean, .before = 17, .after = -1, .complete = TRUE),
         raxpa_2W = slide_dbl(ex_pass_against, mean, .before = 2, .after = -1, .complete = TRUE),
         raxpa_4W = slide_dbl(ex_pass_against, mean, .before = 4, .after = -1, .complete = TRUE),
         raxpa_8W = slide_dbl(ex_pass_against, mean, .before = 8, .after = -1, .complete = TRUE),
         raxpa_17W = slide_dbl(ex_pass_against, mean, .before = 17, .after = -1, .complete = TRUE),
         raxpla_2W = slide_dbl(ex_plays_against, mean, .before = 2, .after = -1, .complete = TRUE),
         raxpla_4W = slide_dbl(ex_plays_against, mean, .before = 4, .after = -1, .complete = TRUE),
         raxpla_8W = slide_dbl(ex_plays_against, mean, .before = 8, .after = -1, .complete = TRUE),
         raxpla_17W = slide_dbl(ex_plays_against, mean, .before = 17, .after = -1, .complete = TRUE),
         rwxprf_2W=slide_dbl(.x=ex_pct_for,.y=plays_for,.f=~weighted_xprf_function(.x,.y),
                            .before=2,.after=-1,.complete=TRUE),
         rwxprf_4W=slide_dbl(.x=ex_pct_for,.y=plays_for,.f=~weighted_xprf_function(.x,.y),
                            .before=4,.after=-1,.complete=TRUE),
         rwxprf_8W=slide_dbl(.x=ex_pct_for,.y=plays_for,.f=~weighted_xprf_function(.x,.y),
                            .before=8,.after=-1,.complete=TRUE),
         rwxprf_17W=slide_dbl(.x=ex_pct_for,.y=plays_for,.f=~weighted_xprf_function(.x,.y),
                            .before=17,.after=-1,.complete=TRUE),
         rwxpra_2W=slide_dbl(.x=ex_pct_against,.y=plays_against,.f=~weighted_xpra_function(.x,.y),
                            .before=2,.after=-1,.complete=TRUE),
         rwxpra_4W=slide_dbl(.x=ex_pct_against,.y=plays_against,.f=~weighted_xpra_function(.x,.y),
                            .before=4,.after=-1,.complete=TRUE),
         rwxpra_8W=slide_dbl(.x=ex_pct_against,.y=plays_against,.f=~weighted_xpra_function(.x,.y),
                            .before=8,.after=-1,.complete=TRUE),
         rwxpra_17W=slide_dbl(.x=ex_pct_against,.y=plays_against,.f=~weighted_xpra_function(.x,.y),
                            .before=17,.after=-1,.complete=TRUE)) %>%
  ungroup()

#View(team_rolling_averages)
```


### Merging our Datasets ###


```{r}
# Merging Home Stats

home_df <- schedule_data %>%
  left_join(team_rolling_averages, by = c("home_team"="posteam","season"="season","week"="week"))

# Merging Away Stats

merged_df <- home_df %>%
  left_join(team_rolling_averages, by = c("away_team"="posteam","season"="season","week"="week"))

# Renaming our Variables

merged_df <- merged_df %>%
  rename_with(~ gsub("\\.x$", "_home", .), ends_with(".x")) %>%
  rename_with(~ gsub("\\.y$", "_away", .), ends_with(".y"))

merged_df$home_cover <- ifelse(merged_df$result > merged_df$spread_line, 1, 0)

merged_df$home_win <- ifelse(merged_df$result > 0, 1, 0)

# View the result

#View(merged_df)
```


### Dropping the Current Week Variables ###


```{r}
merged_df <- merged_df %>% select(-"points_for_home",-"yards_for_home",-"plays_for_home",-"avg_epa_for_home",
                                  -"success_rate_for_home",-"pass_attempts_for_home",-"run_attempts_for_home",
                                  -"pass_rate_for_home",-"points_against_home",-"yards_against_home",
                                  -"plays_against_home",-"avg_epa_against_home",-"success_rate_against_home",
                                  -"pass_attempts_against_home",-"run_attempts_against_home",
                                  -"pass_rate_against_home",-"points_for_away",-"yards_for_away",
                                  -"plays_for_away",-"avg_epa_for_away",-"success_rate_for_away",
                                  -"pass_attempts_for_away",-"run_attempts_for_away",
                                  -"pass_rate_for_away",-"points_against_away",-"yards_against_away",
                                  -"plays_against_away",-"avg_epa_against_away",-"success_rate_against_away",
                                  -"pass_attempts_against_away",-"run_attempts_against_away",
                                  -"pass_rate_against_away",
                                  -"old_game_id",-"gsis",-"nfl_detail_id",-"pfr",-"pff",-"espn",-"ftn",
                                  -"ex_runs_for_home",-"ex_pass_for_home",-"ex_plays_for_home",
                                  -"ex_pct_for_home",-"ex_runs_against_home",-"ex_pass_against_home",
                                  -"ex_plays_against_home",-"ex_pct_against_home",
                                  -"ex_runs_for_away",-"ex_pass_for_away",-"ex_plays_for_away",
                                  -"ex_pct_for_away",-"ex_runs_against_away",-"ex_pass_against_away",
                                  -"ex_plays_against_away",-"ex_pct_against_away")

#View(merged_df)
```


### Separating the Future Data ###


```{r}
df_future <- merged_df %>% filter(gameday >= Sys.Date())

merged_df <- merged_df %>% filter(gameday < Sys.Date())

#View(df_future)
```


### Removing our Playoff Data ###


```{r}
table(merged_df$game_type)

merged_df_corr <- merged_df %>% filter(game_type == "REG")

table(merged_df_corr$game_type)

#View(merged_df_corr)
```


### Data Standardization ###


```{r}
# Standardization function for data.table
standardize_dt <- function(dt, exclude_cols) {
  # Identify numeric columns to standardize
  numeric_cols <- setdiff(names(dt)[sapply(dt, is.numeric)], exclude_cols)
  
  # Apply standardization
  dt[, (numeric_cols) := lapply(.SD, scale), .SDcols = numeric_cols]
}

# List of columns to exclude
exclude_columns <- c("home_cover","home_win","away_score","home_score","away_rest","home_rest","week","season",
                     "result")

# Apply standardization
data_standardized <- standardize_dt(merged_df_corr, exclude_cols = exclude_columns)

# Inspect the standardized data
summary(data_standardized)
```


### Splitting the Data into Train, Test, and Validation ###


```{r}
set.seed(123)  # For reproducibility
sample_index <- sample(1:nrow(merged_df_corr), size = 0.7 * nrow(merged_df_corr))  # 70% for training

train <- merged_df[sample_index, ]
test <- merged_df[-sample_index, ]

#View(train)
#View(test)
```


### Reformatting our Training Set ###


```{r}
train <- train %>% select(-"game_type",-"away_score",-"home_score",-"overtime",-"total",
                          -"surface",-"temp",-"wind",-"spread_line",-"home_moneyline",-"away_moneyline",
                          -"week",-"season",-"away_spread_odds",-"home_spread_odds",-"total_line",-"under_odds",
                          -"over_odds",-"game_date_home",-"game_date_away",-"gameday",-"game_id",-"stadium",
                          -"stadium_id",-"location", -"result", -"home_win", -"weekday")

train <- na.omit(train)

#View(train)
```



### Fitting out Linear Regression Model ###


```{r}
# Fit logistic regression model
full_model <- glm(home_cover ~ ., data = train, family = binomial)

# Fit a null model (only the intercept)
null_model <- glm(home_cover ~ 1, data = train, family = binomial)

# Perform stepwise selection
stepwise_model <- step(null_model, 
                       scope = list(lower = null_model, upper = full_model), 
                       direction = "forward")

# Summary of the selected model
summary(stepwise_model)

```


### Checking the Model Assumptions ###


```{r}
#Linearity
plot(stepwise_model$fitted.values, stepwise_model$residuals)
abline(h = 0, col = "red")

#Normality of Residuals
qqnorm(stepwise_model$residuals)
qqline(stepwise_model$residuals, col = "red")

#Homoscedasticity
plot(stepwise_model$fitted.values, abs(stepwise_model$residuals))
abline(h = 0, col = "red")

#Multicollinearity
vif(stepwise_model)
```


### Determining Optimal Cutpoint Threshold ###


```{r}
#install.packages("pROC")
library(pROC)

# Generate ROC curve
roc_curve <- roc(test$home_cover, test$pred_prob)

# Determine the optimal threshold using Youden's J statistic
optimal_cutpoint <- coords(roc_curve, "best", ret = "threshold", best.method = "youden")
print(optimal_cutpoint)
```


### Predictions ###


```{r}
#install.packages("caret")
library(caret)

test$pred_prob <- predict(stepwise_model, newdata = test, type="response")

test$pred_class <- ifelse(test$pred_prob > 0.5647559, 1, 0)

test_table <- test %>% select("game_id","season","week","home_team","away_team","home_cover",
                              "spread_line","pred_prob","pred_class")

test_table <- na.omit(test_table)

test_table$home_cover <- factor(test_table$home_cover)
test_table$pred_class <- factor(test_table$pred_class)

View(test_table)

# Confusion matrix
#table(Predicted = test_table$pred_class, Actual = test_table$home_win)

# Create confusion matrix
conf_matrix <- confusionMatrix(
  factor(test_table$pred_class), 
  factor(test_table$home_cover), 
  positive = "1"  # Specify the positive class
)

# Print confusion matrix and metrics
print(conf_matrix)
```


### Yardstick Confusion Matrix ###


```{r}
#install.packages("yardstick")
#install.packages("tibble")
library(yardstick)
library(tibble)

# Compute confusion matrix and metrics
conf_matrix <- test_table %>%
  conf_mat(truth = home_win, estimate = pred_class)

# Print confusion matrix
print(conf_matrix)

# Generate metrics like accuracy, sensitivity, specificity
metrics <- conf_matrix %>%
  summary()

# Install and load reactable
#install.packages("reactable")
library(reactable)

# Convert confusion matrix to a data frame
conf_matrix_df <- as.data.frame(conf_matrix$table)

# Create an interactive table
reactable(conf_matrix_df, 
          columns = list(
            Prediction = colDef(name = "Prediction"),
            Actual = colDef(name = "Actual"),
            n = colDef(name = "Count")
          ),
          bordered = TRUE,
          striped = TRUE,
          highlight = TRUE)
```


### Predicting this Week's Games ###


```{r}
upcoming_week <- df_future %>% filter(week == 13)

#View(upcoming_week)

upcoming_week$pred_prob <- predict(stepwise_model, newdata = upcoming_week, type="response")

upcoming_week$pred_class <- ifelse(upcoming_week$pred_prob > 0.5647559, 1, 0)

uw_table <- upcoming_week %>% select("game_id","season","week","home_team","away_team","home_cover",
                              "spread_line","pred_prob","pred_class")

View(uw_table)
```




































